---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

 <!-- badges: start -->
[![Lifecycle: deprecated](https://img.shields.io/badge/lifecycle-deprecated-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#deprecated)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)

<!-- badges: end -->

# creelr
 
An R package to Analyse Angler Creel Survey Data. 
Currently only the Traditional Access Design for One Access Site is implemented.

To install the latest development version from [GitHub](https://github.com/poissonconsulting/creelr)
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/creelr")
```

## Citation

```{r, comment="", echo=FALSE}
citation(package = "creelr")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/creelr/issues).

[Pull requests](https://github.com/poissonconsulting/creelr/pulls) are always welcome.

## Code of Conduct

Please note that the creelr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
